Thermodynamic Structure of the Solar Corona: Tomographic Reconstructions and MHD Modeling

### 2019-12-03 lloveras_2020.tex
graficos de energia

  I - Small-closed field lines. Small meaning with apex within the DEMT range of heights. %This class thoroughly probes the inner core of the Streamer belt, where most of the DOWN loops showed up before, and will show up now.

  II - Large-closed field lines. Large meaning their apex surpasses the DEMT range of heights. This class is mostly populated by very large trans-equatorial field lines forming the "envelope" of the Streamer belt.

 III - Open field lines.

@@

>>>>

  0 - Small-closed field lines footlat $<30$ y gradt neg. where most of the DOWN loops showed up before

  I - Small-closed field lines. Small meaning with apex within the DEMT range of heights. gradt pos
   %This class thoroughly probes the inner core of the Streamer belt, where most of the DOWN loops showed up before, and will show up now.

  II - Large-closed field lines. Large meaning their apex surpasses the DEMT range of heights. This class is mostly populated by very large trans-equatorial field lines forming the "envelope" of the Streamer belt. footlat $>30$ y gradt pos

 III - Open field lines. footlat $>60$ y gradt pos

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2082_ccenergia.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2082_cgenergia.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2208_ccenergia.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2208_cgenergia.eps}
\caption{Statistical results of the loop integrated energy flux quantities $\phi_r,\phi_c, and \phi_h$ for CR2082 (top) and CR2208 (bottom). Left/right panels correspond to the type 0-1 and type 2 respectively \textcolor{red}{el tipo 2 tmb tiene down! Aca hay que tomar una desicion para no marear al lector! Pero lo dejo asi internamente para compararlo con figura 5 y 6 del aper de Mac Cormack}}
\label{gradt_demt}
\end{center}
\end{figure}
